\documentclass[11pt,letterpaper]{article}

\usepackage[letterpaper,left=0.5in,right=0.5in,top=0.5in,bottom=0.12in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{newtxtext,newtxmath}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{array}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{label=$\diamond$,leftmargin=1.55em,labelsep=0.55em,itemsep=0.18em,topsep=0.12em,parsep=0pt,partopsep=0pt}
\renewcommand{\baselinestretch}{1.05}

\newcommand{\basefont}{\fontsize{11.5pt}{13.65pt}\selectfont}
\newcommand{\namefont}{\fontsize{25pt}{27pt}\selectfont}
\newcommand{\contactfont}{\fontsize{11.5pt}{13pt}\selectfont}

\newcommand{\sectionlabel}[1]{%
  {\centering\bfseries\MakeUppercase{#1}\par}
}

\newcommand{\sectionrule}{\vspace{0.6em}\noindent\rule{\textwidth}{0.5pt}\vspace{0.6em}}

\newcommand{\resrow}[2]{%
  \noindent
  \begin{minipage}[t]{1.06in}
    \sectionlabel{#1}
  \end{minipage}%
  \hspace{0.16in}%
  \begin{minipage}[t]{5.88in}
    \justifying #2
  \end{minipage}\par
}

\newcommand{\entryline}[2]{\noindent #1\hfill #2\par}
\newcommand{\jobline}[2]{\noindent #1\hfill #2\par}

\begin{document}
\basefont

\begin{center}
{\namefont\bfseries NICOLAS NASTRI}
\end{center}

\vspace{-0.35cm}
\begin{center}
{\contactfont\bfseries Washington, DC \;|\; \href{mailto:nn3495a@american.edu}{nn3495a@american.edu} \;|\; +1 (781) 752-8377}
\end{center}

\vspace{-0.75cm}
\begin{center}
{\contactfont
\href{https://www.linkedin.com/in/niconastri/}{\faLinkedin\ linkedin.com/in/niconastri} \;|\;
\href{https://niconastri.com/}{\faGlobe\ niconastri.com} \;|\;
\href{https://github.com/ngnastri10}{\faGithub\ github.com/ngnastri10}}
\end{center}

\vspace{.3cm}

\resrow{Executive\\Summary}{%
\begin{itemize}
    \item Economist and data analyst with experience in energy policy, and applied microeconomics.
    \item Skilled in Stata, Python, R, SQL, and ArcGIS for empirical research and decision support.
    \item Native English \& Spanish speaker; Advanced French speaker.
\end{itemize}}

\sectionrule

\resrow{Education}{%
\entryline{\textbf{American University} -- Ph.D. in Economics}{2022 -- 2027 (Expected Graduation)}
\entryline{\textbf{Georgetown University} -- M.A. in Political Economy}{2018-2019}
\entryline{\textbf{Boston University} -- B.A. in Economics \& International Relations}{2012-2016}}

\sectionrule

\resrow{Work\\Experience}{%
\jobline{\textbf{EPRI -- Sustainability Data Analyst}, Washington D.C.}{August 2025 -- December 2025}
\begin{itemize}
    \item Created a product used by electric utility clients to evaluate how different sustainability frameworks align with eight core value areas.
    \item Queried and processed electric utility data in SQL and Python, cleaning and structuring inputs to benchmark sustainability practices and support tool development.
\end{itemize}

\vspace{0.65em}
\jobline{\textbf{The World Bank -- Internship Program (BIP)}, Washington D.C.}{April 2025 -- July 2025}
\noindent{\itshape Subnational Business Ready Unit -- Electricity\par}
\begin{itemize}
    \item Developed an Excel tool assessing electricity cost of service under varying assumptions.
    \item Contributed to a methodology handbook extending B-READY to evaluate distributed solar.
    \item Researched electricity laws to assess alignment with B-READY criteria in country reports.
\end{itemize}

\vspace{0.65em}
\jobline{\textbf{Sustainable Capital Advisors -- Research Fellow}, Washington D.C.}{2023 -- 2025}
\begin{itemize}
    \item Designed and built the ``Geographic Readiness Tool,'' a county level analysis platform evaluating solar energy and EV economic potential to guide client investment decisions.
\end{itemize}

\vspace{0.65em}
\jobline{\textbf{Center For Retirement Research -- Research Associate}, Newton MA}{2020 -- 2022}
\begin{itemize}
    \item Performed statistical analysis on retirement policies using Stata, including descriptive statistics, regression-based causal estimation, and literature reviews.
    \item Obtained Special Sworn Status (SSS) to analyze restricted US Census Bureau data.
\end{itemize}

\vspace{0.65em}
\jobline{\textbf{Inter-American Dialogue -- Research Intern}, Washington D.C.}{June 2019 -- August 2019}
\noindent{\itshape Energy, Climate Change, \& Extractive Industries Program\par}}

\sectionrule

\resrow{Research}{%
\noindent\textbf{Works in Progress}\par
\begin{itemize}
    \item ``Carbon Border Adjustments and Directed Technical Change'' (JMP)
    \item ``Climate Risk, Innovation, and the Diffusion of Green Technologies'' \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=6516621}{(SSRN Link)}
    \item ``ESG Disclosure Mandates and Emissions in Global Value Chains''
\end{itemize}}

\sectionrule

\resrow{Honors \&\\Awards}{%
\begin{itemize}
    \item Frank M. Tamagna Scholarship (2026)
    \item Econometrics Paper Competition (AU Economics Department)
\end{itemize}}

\sectionrule

\resrow{Technical\\Skills}{%
\begin{itemize}
    \item Programming: Stata, R, Python, SQL, ArcGIS, Latex, Linux HPC Cluster, GitHub, HTML
    \item Datasets: Bloomberg, WITS, PATSTAT, MSCI ESG, FactSet, Input-Output Tables
    \item Methods: Causal Inference, Machine Learning, Geo-Spatial Analysis, Web Scraping
\end{itemize}}

\end{document}
